%% Submissions for peer-review must enable line-numbering 
%% using the lineno option in the \documentclass command.
%%
%% Preprints and camera-ready submissions do not need 
%% line numbers, and should have this option removed.
%%
%% Please note that the line numbering option requires
%% version 1.1 or newer of the wlpeerj.cls file, and
%% the corresponding author info requires v1.2

\documentclass[fleqn,10pt,lineno]{wlpeerj} % for journal submissions
% \documentclass[fleqn,10pt]{wlpeerj} % for preprint submissions


\newif\ifappendixStyle
\appendixStylefalse

\usepackage[hyphens]{url}
\urlstyle{same}


\usepackage{afterpage}

\usepackage{pdflscape}

\usepackage{array}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}} %% To centre tables with p columns. Use P{X.Xcm}
\newcolumntype{B}[1]{>{\centering\arraybackslash}b{#1}} 

\usepackage{textcomp} %% For tildes
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{subcaption}
\graphicspath{{"\string~/Box Sync/help/PhD_copy/Wildlife Garden/HighQualityFigures/"}{"\string~/Box Sync/help/PhD_copy/Wildlife Garden/MetaAnalysis/Figures/"}{"\string~/Box Sync/help/PhD_copy/Wildlife Garden/PlantsDatabase/Figures/"}}
\usepackage[font=small,labelfont=bf]{caption}

\title{Estimating the potential biodiversity impact of redeveloping small urban spaces: the Natural History Museum's grounds as a case study}

\author[1,2]{Helen R. P. Phillips}
\author[2]{Sandra Knapp}
\author[1,2]{Andy Purvis}
\affil[1]{Imperial College London, Silwood Park Campus, Buckhurst Rd, Ascot, SL5 7QN}
\affil[2]{Natural History Museum, Department of Life Sciences, Cromwell Rd, London SW7 5BD}
\corrauthor[1]{Helen R. P. Phillips}{hp1111@ic.ac.uk}

% \keywords{Keyword1, Keyword2, Keyword3}

\begin{abstract}
\textbf{Background:} With the increase in human population, and the growing realisation of the importance of urban biodiversity for human wellbeing, the ability to predict biodiversity loss or gain as a result of land use change within an urban settings is important. Most models that link biodiversity and land use are at too coarse a scale for informing decisions, especially those related to planning applications. Using the grounds of the Natural History Museum, London, as a case study, we show how methods used in global models can be applied to smaller spatial scales to inform urban planning. 

\textbf{Methods:} Data were extracted from relevant primary literature where species richness had been recorded in more than one habitat type within an urban setting. As within-sample species richness will increase with habitat area, species richness estimates were also converted to species density using theory based on the species area relationship. Mixed-effects models were used to model the impact on species richness and species density of different habitat types, and to estimate these metrics in the current grounds and under the proposed plans. We used three assumptions on how within-sample diversity scales with habitat area as a sensitivity analysis. A pre-existing plant database was also used to estimate changes in species composition across different habitats.

\textbf{Results:} Analysis showed that the proposed plans could result in a net biodiversity increase of 14.05\% across the NHM grounds, when local species richness was modelled. The least optimistic result showed only an 11.17\% increase in biodiversity, when species density was the response metric and changes in habitat area were accounted for. Plant community composition was relatively similar between the habitats currently within the grounds.

\textbf{Discussion:} The proposed plans to the NHM grounds are estimated to result in a net gain in biodiversity, through increased number and extent of high-diversity habitats. In future, our method could be improved by incorporating ecological survey data collected for the purpose (if resources permit) and by expanding the data sufficiently to allow modelling of the temporal dynamics of biodiversity change after habitat disturbance and creation. Even in its current form, the method produces transparent quantitative estimates, grounded in ecological data and theory, that can be used to inform planning decisions.

\end{abstract}

\begin{document}

\flushbottom
\maketitle
\thispagestyle{empty}

\input{./../wlg-main/wlg-main}



\bibliography{./../../../PhD_BibTex/PhD-refs}
\end{document}